### 2018-09-05 Chapters/Chapter1.tex
Add Melendley and some text

\chapter{AFM spinotronics}

>>>>

\chapter{AFM spinotronics}
Historically ferromagnets have been widely studied as spintronic elements. However, today, the development of information technology demands devices with high storage density, high energy efficiency and high write/read speeds. Therefore, controlling magnetically ordered systems on subpicosecond timescales is currently a widely studied area. It has been shown that circularly polarized femtosecond laser pulses can be used to control the spin dynamics in magnets \cite{Kimel2005}. Antiferromagnetic metals have become an interesting alternative due to their rigidity to external magnetic field, and the abscence of stray field.

Antiferromagnetism materials exhibits no net magnetization since the spins in the material align antiparallel to each other. Historiacally, ferromagnetic materials have been more interesting for practical applications, however recent researches show that antiferromagnetism has promising application in next generation spintronic devices. Controlling magnetically ordered systems on subpicosecond timescales.

### 2018-09-05 main.tex
Bloch Theorem and apendix1
Added Wannier
Derive Hubbard
Heisenber model
style changes
Add title
chap 2
chap 2
introchap
Add Melendley and some text

\usepackage{mathpazo} % Use the Palatino font by default

@@

\addbibresource{example.bib} % The filename of the bibliography

@@

\thesistitle{Thesis Title} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Dr. James \textsc{Smith}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{Doctor of Philosophy} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Juan Manuel Losada} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

@@

@@

\include{Chapters/Chapter1}
%\include{Chapters/Chapter2} 
%\include{Chapters/Chapter3}
%\include{Chapters/Chapter4} 
%\include{Chapters/Chapter5}

>>>>

\usepackage{mathpazo} % Use the Palatino font by default
\usepackage{appendix}
\usepackage{chngcntr}
\usepackage{etoolbox}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{braket}

@@

\addbibresource{MT.bib} % The filename of the bibliography

@@

\thesistitle{Ultrafast manipulation of exchange DMI in antiferromagnetic insulators} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Dr. James \textsc{Smith}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{Doctor of Philosophy} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Juan Manuel Losada} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

@@

% Start of subappendices environment
\AtBeginEnvironment{subappendices}{%
\chapter*{Appendices}
\addcontentsline{toc}{chapter}{Appendices}
\counterwithin{figure}{section}
\counterwithin{table}{section}
}

% End of subappendices environment
\AtEndEnvironment{subappendices}{%
\counterwithout{figure}{section}
\counterwithout{table}{section}
}

\newcommand{\bs}[1] {\boldsymbol{#1}}

@@

\include{Chapters/Chapter1}
\include{Chapters/Chapter2} 
\include{Chapters/Chapter3}
%\include{Chapters/Chapter4} 
%\include{Chapters/Chapter5}
